### 2023-01-05 README.Rmd
updated readme, fuzzy name matching,

---
output: github_document
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

@@

Categorical             |  Sequential | Diverging
:-------------------------:|:-------------------------:|:-------------------------:
[![](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png)](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png) | [![](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png)](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png) | [![](https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png)]((https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png))

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support several types: *categorical* (qualitative) palettes, *sequential* palettes, *diverging* palettes, and *bivariate* palettes (divided into three types). In the near future, more palette types may be added, such as *cyclic* and *hierarchical*.

@@

**cols4all** will be available on CRAN soon. Until then it can be installed using:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mtennekes/cols4all")
```

```{r, echo=FALSE}
getwd()
devtools::load_all(".")
```

@@

Navigation through the color palettes is easy via the GUI shown above, which is started with:

```{r, eval=FALSE}
library(cols4all)
# For the GUI, shiny, shinyjs, and kableExtra are required
# install.packages(c("shiny", "shinyjs", "kableExtra"))
c4a_gui()
```

Besides browsing through palettes, it is also easy to copy color codes to the clipboard, either by selecting the hidden text in the color tables or by clicking on the icons at the right-hand-side:

![](https://user-images.githubusercontent.com/2444081/156849917-59af1dc1-ee5e-40be-bf87-5c7384351ae0.png){width=50%}

Selecting a palette is easy:

@@

# find names of hcl palettes that are diverging
c4a_palettes(type = "div", series = "hcl")

@@

* `c4a_gui` GUI (shiny app) to see and analyse the palettes
* `c4a` Get the colors of a palette

@@

* `c4a_palettes` Get available palette names
* `c4a_series` Get available series
* `c4a_meta` Get meta information (such as type and maximum number of colors )
* `c4a_ls` Environment via which palette names can be browsed with auto-completion (using `$`)

@@

* `c4a_palettes_add` Add color palettes
* `c4a_palettes_remove` Remove color palettes
* `c4a_sysdata_import` Import system data
* `c4a_sysdata_export` Export system data

@@

* Colors for missing values are made explicit. For this, either a greyscale color that is already contained in the palette is used, or a greyscale color is selected that is distinguisable, also for people with color vision deficiency.

* Palettes are made consistent with each other. For instance, sequential palettes (except for spectral/rainbow palettes) all start with the lightest color and end with the darkest color. Furthermore, black and white are removed from most categorical palettes for practical reasons: white or light grey is almost always used as background color and black for annotation.

* The GUI enables users to analyse characteristics of color palettes, such as color-blind-friendliness, harmony, and the presence of intense colors.

@@

* It will be possible to submit an own series of color palettes.

>>>>

---
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(more, x[lines], more)
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })
```

@@

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support several types: *categorical* (qualitative) palettes, *sequential* palettes, *diverging* palettes, and *bivariate* palettes (divided into four subtypes).

@@

**cols4all** will be available on CRAN in January or February this year (2023). Until then it can be installed using:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("mtennekes/cols4all", dependencies = TRUE)
```

```{r, echo=FALSE, message=FALSE}
devtools::load_all(".")
```

@@

Load the package:

```{r, eval=FALSE}
library(cols4all)
```

The main tool is a dashboard, which is started with:

```{r, eval=FALSE}
c4a_gui()
```

![https://user-images.githubusercontent.com/2444081/210850914-cdb8a128-1b8a-4900-94d0-dfa6ca449585.png](https://user-images.githubusercontent.com/2444081/210850914-cdb8a128-1b8a-4900-94d0-dfa6ca449585.png)

What palettes are available?

```{r, output.lines = 10}
# All loaded palettes
c4a_palettes()
```

```{r}
# Diverging palettes from the 'hcl' series
c4a_palettes(type = "div", series = "hcl")
```

Give me the colors!

@@

@@

*   `c4a_gui` Dashboard for analyzing the palettes
*   `c4a` Get the colors from a palette

@@

*   `c4a_palettes` Get available palette names
*   `c4a_series` Get available series names
*   `c4a_citation` Show how to cite palettes (with bibtex code).
*   `c4a_info` Get information from a palette, such as type and maximum number
    of colors
*   `.P` Environment via which palette names can be browsed with
    auto-completion (using `$`)

@@

*   `c4a_data` Build color palette data
*   `c4a_load` Load color palette data
*   `c4a_sysdata_import` Import system data
*   `c4a_sysdata_export` Export system data

@@

*	Color palettes are characterized and analysed. Properties such as color blindness, fairness (whether colors stand out about equally), and contrast are determined for each palette.

*	Bivariate color palettes are available (besides the three main palette types: categorical, sequential, and diverging).

*	Own color palettes can be loaded and analysed.

*	Color for missing values are made explicit.

*   Palettes are made consistent with each other to enable comparison. For instance, black and white are (by default) removed from categorical palettes. Another standard that we adapt to is that all sequential palettes go from light to dark and not the other way round.

@@

*	There are a couple of exporting options, including (bibtex) citation.
